Something fancy...

### 2020-01-17 draft.tex

                       \documentclass[prb,twocolumn,amsmath,longbibliography,amssymb,superscriptaddress]{revtex4-1}

@@

\section{Introduction.}

\section{Model}

>>>>

\documentclass[twocolumn,amsmath,longbibliography,amssymb,superscriptaddress]{revtex4-1}

@@

\section{Introduction}

topological phases --- interacting and non-interacting

How to identify interesting phases?--- entanglement entropy, entanglement spectrum

Kitaev honeycomb model as example of entanglement spectrum

What information is encoded in the ES? How to extract it?

naively resp. easily accessible: information about edge spectrum

But, other information can be accessed as well : e.g. compactification radius

in general, still unclear what info is encoded and whether it can uniquely specify the topological order at hand

situation not much better for non-interacting systems--- even here, unclear what information is encoded and how one can read it off from the spectrum

here, we show that the information about the Berry phase can be completely recovered from the entanglement spectrum and provide a simple formula to do so

This can be related to earlier attempts, REFS

\section{Model.}
